---
title: "MapReduce with Hadoop Assignment 2 - Report"
author: "Neelesh and Habiba"
output: html_document
---
### Implementation details for the MapReduce:

### Mapper
`CsvMapper` is the class which extends Mapper and takes the following for key,value pair :
key - Object which has a file
value - rows in csv file that the key contains.
The Mapper returns the following:
Key - Airline code
Value - String with year, month and count concatenated

#### Reducer
`MeanReducer` class will iterate over `Iterable<Text>` and calculates average ticket price for each airline per month. The reducer will write to the context, airline code along with monthly counts, mean price and month number.

#### Output of MapReduce job
The output file will contain rows as below:  
```{r, eval=FALSE}
AA	513.6958373	1	1115470
AA	505.0351644	2	1115470
AA	503.9140978	3	1115470
....
```
The first column is the airline,second is average ticket price per month, third column is Month number and the final is count of flights the airline runs in total. This data is redundantly returned by the reducer.

### Running the program in pseudo-distributed mode
#### Prerequisites
Current directory should have the folder 'all' with all the gzip files in it.
####Note: This will clear the hadoop filesystem. So make sure your data is taken care of.
```{r, eval=FALSE}
# Execute the following make command from inside the submission folder.
make pseudo
```


### Running the program in cloud (AWS EMR)
#### Prerequisites
Current directory should have the folder 'all' with all the gzip files in it.
####Note: This will create a new bucket in the s3 filesystem. 
```{r, eval=FALSE}
# Execute the following make command from inside the submission folder
# Make sure that aws command line client and authentication keys are setup
make emr
```
  
### Results - Plot

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
library(ggplot2)
## ---- outputplot ----
args<-commandArgs(trailingOnly = TRUE)
foldername <- args[1]
#"/Users/ummehabibashaik/Documents/Mapreduce/HW2/Output_Local/input"
setwd(foldername)
files<-list.files()
outputData<-c()
for(i in 1:length(files)){
  outputData <- rbind(outputData,read.table(file=files[i], header=FALSE, sep="\t"))
}
colnames(outputData) <- c("Airline","TicketPrice","Month","Count")
uniqueList<-unique(outputData[c(1,4)])
uniqueList<-uniqueList[order(uniqueList$Count,decreasing=TRUE),]
topAirlines <- head(uniqueList[1],10)

outputDataFiltered<-outputData[(outputData$Airline %in% topAirlines$Airline),]
#ggplot(data = outputDataFiltered, aes(x=Month, y=TicketPrice)) + geom_line(aes(colour=Airline))
#ggsave(filename = '../Plotnew.png',plot=last_plot())
```

Following graph shows average ticket prices for each month for top 10 airline carriers that were active in 2015:

```{r, echo=FALSE}
# Display plot in the report --------------------------------

# Plot average ticket price for each month for each airline

# NOTE: 
# scale_shape_manual is required because ggplot will automatically assign only
# 6 shapes to 6 different Carriers. We have more than 6 carriers, which requires 
# manual setting.    
ggplot(data = outputDataFiltered, aes(x=Month, y=TicketPrice)) + geom_line(aes(colour=Airline))
```