---
title: "Linear Regression - Assignment 4 Report"
author: "Neelesh and Habiba"
output: html_document
---


### Implementation details for the MapReduce:

### Shell script
We created a shell script which invokes calls to
1. Hadoop program for MapReduce in EMR mode
2. EMR commandline call to create a cluster and run the step.

#### Inputs
Input - The .gz files provided in the all folder are placed in input folder

#### Output from shell script
Output files from the programs will be written as below to output/
```{r, eval=FALSE}
    Report.pdf
    ...
```

### Running the shell script
#### Prerequisites
Input files should be placed in input

```{r, eval=FALSE}
# Execute the script in the following way
make Regression
```

#### Implementation Details of Linear Regression
```{r, eval=FALSE}
1. Using mapReduce, found out the sane records from all the files.
2. Sent the sane records from 2010-2014 as output with Carrier as Key and Distance, CRS_Elapsed_Time and AVG_Price as Value.
3. Using the output from MapReduce we make linear models for all the 13 Carriers.
4. We plot 2 graphs for each Carrier one using Avg_Price to Distance and other using Avg_Price to CRS_Elapsed_Time i.e. 26 graphs in total
5. We found that the Distance has better slope than Time for all the carriers and the r-squared error is less for Distance. So Distance is a better variable.

```

###Conclusion
F9 is the cheapest airline. For every airline, we found the avg price at regular interval and added them. F9 has the least summation value.
Distance is a better variable as the Slope of Distance is more than Time for all the Carriers and the summation of r-squared error is less for distance as compared to time.

  
### Results - Plot

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
library(ggplot2)
library(caret)
args<-commandArgs(trailingOnly = TRUE)
foldername <- args[1]
#setwd(foldername)
files<-list.files(path="/Users/ummehabibashaik/Documents/Mapreduce/HW4/src/pseudo/output",pattern="part-r-",full.names = TRUE)
  #dir("/Users/ummehabibashaik/Documents/Mapreduce/HW4/src/pseudo/output/", pattern='part-r-', full.names = TRUE)
newData<-c()
for(i in 1:length(files)){
  newData <- rbind(newData,read.table(file=files[i], header=FALSE, sep="\t"))
}

#Loading Data
colnames(newData) <- c("AIRLINE","AVG_TICKET_PRICE","DISTANCE","CRS_ELAPSED_TIME")

#Data cleansing - removing null values
CleansedData <- na.omit(newData)
CleansedData$CRS_ELAPSED_TIME <- as.integer(CleansedData$CRS_ELAPSED_TIME)
summary(CleansedData)

uniqueList<-unique(CleansedData[c('AIRLINE')])

```

Following graph shows time taken for each configuration to run with different input sizes:

```{r, echo=FALSE}
# Display plot in the report --------------------------------

# Plot average ticket price for each month for each airline

# NOTE: 
# scale_shape_manual is required because ggplot will automatically assign only
# 6 shapes to 6 different Carriers. We have more than 6 carriers, which requires 
# manual setting.    
airline_prices <- data.frame(AIRLINE=character(),PRICE=integer(),stringsAsFactors=FALSE) 
for (airline in uniqueList$AIRLINE){
  #airline<-'F9'
  filteredData <- CleansedData[CleansedData$AIRLINE == airline,]
  
  #Model1: Training Linear model with Distance
  plot.x <- qplot(y=AVG_TICKET_PRICE, x=DISTANCE, data=filteredData)
  model.x <- lm(AVG_TICKET_PRICE ~ DISTANCE, filteredData)
  prices <- predict(model.x,data.frame(DISTANCE=(c(100,500,1000))),interval="prediction")
  airline_prices <- rbind(airline_prices,data.frame("AIRLINE"=airline, "PRICE"=sum(prices[,"fit"])))
  coef(model.x)
  print(plot.x + geom_abline(intercept=coef(model.x)[1],slope=coef(model.x)[2],col='red')+ xlab("Distance")+ ylab("Ticket Price"))
  #ggsave(filename = paste(airline,"_dist",".png",sep=""),plot=plt)
  
  #Model2 Training Linear model with CRS_ELAPSED_TIME
  plot.x2 <- qplot(y=AVG_TICKET_PRICE, x=CRS_ELAPSED_TIME, data=filteredData)
  model.x2 <- lm(AVG_TICKET_PRICE ~ CRS_ELAPSED_TIME, filteredData)
  coef(model.x2)
  print(plot.x2 + geom_abline(intercept=coef(model.x2)[1],slope=coef(model.x2)[2],col='red')+ xlab("CRS_ELAPSED_TIME")+ ylab("AVG_TICKET_PRICE"))
  #ggsave(filename = paste(airline,"_time",".png",sep=""),plot=plt2)
  
}

sortedList<-airline_prices[order(airline_prices$PRICE,decreasing=FALSE),]
cheapAirline <- head(sortedList[1],1)
print(cheapAirline,row.names=FALSE)
```
